Thermodynamic response functions in a cell fluid model

### 2024-09-02 main_morse_response_functions.tex
yes, under arccos we should have 3, fixed that
add identity alpha_P/K/beta_V = 1

	This dependency can also be expressed explicitly. To achieve this, we combine the equations~\eqref{eq:density} and~\eqref{eq:ro_M} to express the effective chemical potential $M$ as a function of density and temperature:
	\begin{equation}\label{eq:M_nT}
		\bar M = \frac{\rho_{n}}{\beta W(0)} - (\bar n - n_g),
	\end{equation}
	where
	\begin{align} \label{eq:ro_nT}
		 & \rho_{n} = - 2 \left(\frac{g_3^2 - 2g_2 g_4}{g_4^2} \right)^{\frac{1}{2}} \cos \left( \frac{\alpha_n}{3} + \frac{\pi}{3} \right), \\
		 & \alpha_n = \arccos \left( \frac{3}{2} \left( - \frac{g_4^4}{\left( 2 g_2 g_4 - g_3^2\right)^3}\right)^{\frac{1}{2}} (n_g - \bar n)\right). \nonumber
	\end{align}
	{\color{Red} {\bf{NOTE 2: }} Roma: In my opinion, under {\it{arccos}} we should have 3, not $\frac{3}{2}$}

@@

>>>>

	This dependency can also be expressed explicitly. To achieve this, we combine the equations~\eqref{eq:density} and~\eqref{eq:ro_M} to express the effective chemical potential $M$ as a function of density and temperature:
	\begin{equation}\label{eq:M_nT}
		\bar M = \frac{\rho_{n}}{\beta W(0)} - (\bar n - n_g),
	\end{equation}
	where
	\begin{align} \label{eq:ro_nT}
		 & \rho_{n} = - 2 \left(\frac{g_3^2 - 2g_2 g_4}{g_4^2} \right)^{\frac{1}{2}} \cos \left( \frac{\alpha_n}{3} + \frac{\pi}{3} \right), \\
		 & \alpha_n = \arccos \left( \left( - \frac{9 g_4^4}{\left( 2 g_2 g_4 - g_3^2\right)^3}\right)^{\frac{1}{2}} (n_g - \bar n)\right). \nonumber 
	\end{align}
	{\color{Red} {\bf{NOTE 2: }} Roma: In my opinion, under {\it{arccos}} we should have 3, not $\frac{3}{2}$ \color{Green} Oksana: Yes, you are right, I've fixed that }

@@

	\subsection{Relation between response functions}
	The following thermodynamic identity holds between the calculated response functions
	\begin{equation}
		\frac{\alpha_P}{K_T \beta_V} = \frac{\alpha^*_P}{K^*_T \beta^*_V} = 1,
	\end{equation}
	which is easily derived from the cyclic relation between $P$, $V$ and $T$. In our case, this equality is exactly reproduced by substituting explicit expressions for $K_T$, $\alpha_P$, and $\beta_V$ obtained from the equation of state~\eqref{eq:eosMT} (or~\eqref{eq:eosNT}).
